quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-07-01 paper-quollr.Rmd
Added a way to refer crosstalk output with fi-cap

This paper presents the R package, `quollr`, which is useful for understanding how NLDR warps high-dimensional space and fits the data. Starting with an NLDR layout, our approach is to create a wireframe model representation, that can be lifted and displayed in the high-dimensional space (`r knitr::asis_output(if (knitr::is_html_output()) { "[Figure 1](#fig-overview)"} else { "Figure \\@ref(fig:overview)"})`).

@@

htmltools::browsable(
  tagList(
    tags$div(
      id = "fig-overview",  # This is the anchor
      crosstalk::bscols(
        htmltools::div(
          style = "display: grid; grid-template-columns: 1fr 1fr;",
          hex_grid_scurve_int,
          htmltools::div(style = "margin-top: 13px;", scurve_umap_model_vis)
        ),
        device = "xs"
      ),
      tags$p(tags$strong("Figure 1:"), " Algorithm to visualize the 2D model.")
    )
  )
)

@@

```{r, echo=TRUE, eval=knitr::is_html_output()}
show_link_plots(
  point_data = df_exe, 
  edge_data = trimesh
  )
```

@@

Limb muscle cells of mice in @tabula2018 are examined. There are $1067$ single cells, with $14997$ gene expressions. Following their pre-processing, different NLDR methods were performed using ten principal components. Figure \@ref(fig:limb-rmse) (b) is the reproduction of the published plot. The question is whether this accurately represents the cluster structure in the data. Our method can help here, and also help to provide a better $2-\text{D}$ layout, as needed.

>>>>

This paper presents the R package, `quollr`, which is useful for understanding how NLDR warps high-dimensional space and fits the data. Starting with an NLDR layout, our approach is to create a wireframe model representation, that can be lifted and displayed in the high-dimensional space (`r knitr::asis_output(if (knitr::is_html_output()) { "Figure \\@ref(fig:overviewhtml)"} else { "Figure \\@ref(fig:overview)"})`).

@@

```{r overviewhtml, eval=knitr::is_html_output(), fig.cap="algorithm", fig.pos='H'}

overviewfig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr;",
    hex_grid_scurve_int,
    htmltools::div(style = "margin-top: 13px;", scurve_umap_model_vis)
  ),
  device = "xs"
)

class(overviewfig) <- c(class(overviewfig), "htmlwidget")

overviewfig
```

@@

```{r linkerror, echo=TRUE, eval=knitr::is_html_output(), fig.cap="jkjio"}
show_link_plots(
  point_data = df_exe, 
  edge_data = trimesh
  )
```

@@

Limb muscle cells of mice in @tabula2018 are examined. There are $1067$ single cells, with $14997$ gene expressions. Following their pre-processing, different NLDR methods were performed using ten principal components. Figure \@ref(fig:limb-rmse) (b) is the reproduction of the published plot. The question is whether this accurately represents the cluster structure in the data. Our method help to provide a better $2-\text{D}$ layout.

<!-- add function to generate 2D trimesh and the projections (PDF) and langevitour (HTML)-->

### 2025-07-01 paper-quollr.tex
Added a way to refer crosstalk output with fi-cap

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-29-1}

@@

Limb muscle cells of mice in \citet{tabula2018} are examined. There are \(1067\) single cells, with \(14997\) gene expressions. Following their pre-processing, different NLDR methods were performed using ten principal components. Figure \ref{fig:limb-rmse} (b) is the reproduction of the published plot. The question is whether this accurately represents the cluster structure in the data. Our method can help here, and also help to provide a better \(2-\text{D}\) layout, as needed.

>>>>

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-28-1}

@@

Limb muscle cells of mice in \citet{tabula2018} are examined. There are \(1067\) single cells, with \(14997\) gene expressions. Following their pre-processing, different NLDR methods were performed using ten principal components. Figure \ref{fig:limb-rmse} (b) is the reproduction of the published plot. The question is whether this accurately represents the cluster structure in the data. Our method help to provide a better \(2-\text{D}\) layout.
